DRAFT: Social Learning and Shared Belief: The Importance of Bias and Trust for Information Diffusion

### 2014-09-26 paper/paper.tex

We investigate the impact that bias and trust has on how information is diffused within a network of agents.  We use this model to investigate the information diffusion characteristics of 2 different data sets.  We also use our measures of trust to estimate some probability for the real state of the world.  Additionally, we estimate whether certain agents are higher quality than others based on how well they are trusted.  Finally, we consider a measure of risk aversion related to how willing agents are to trust each other.

@@

We examine two novel data sets to investigate this model, the first is a data set of tweets for a list of roughly 3000 media firms in the United States from June to August of 2014.  Additionally, we consider a data set of articles taken from the preprint repository ArXiv.  We build a trust network for both of these data sets based on a number of different measures of bias and use this to investigate our model. To investigate this model we use a graphical variant of the dynamic topic model to estimate trust between agents.

@@

The literature on slant in academia is more limited than in the media case, perhaps because the impact is less apparent.  Much of the literature focuses on divisions of citation networks, though some look at text clustering including one example presented below.  Onder and Tervio look at the division of citation networks into "freshwater" and "saltwater" departments for economics.  They find that the division is very real and significant in a number of cases\footnote{Onder and Tervio.  Is Economics a House Divided?  Analysis of Citation Networks.  2014.}.

>>>>

We investigate the impact that bias and trust has on how information is diffused within a network of news firms.  We use this model to investigate the information diffusion characteristics of a novel data set of tweets form US news firms.  We also use our measures of trust to estimate some probability for the real state of the world.  Additionally, we estimate whether certain agents are higher quality than others based on how well they are trusted.  Finally, we consider a measure of risk aversion related to how willing agents are to trust each other.

@@

We examine two novel data sets to investigate this model, the first is a data set of tweets for a list of roughly 2000 media firms in the United States from June to August of 2014.  We build an trust network for the data set based on a number of different measures of bias and use this to investigate our model. To investigate this model we use a graphical topic model to estimate trust between agents.

@@
